Exploiting Private and Hybrid Clouds for Data-intensive Computing

### 2012-07-31 MSc-dissertation.tex
"Changes in format - cite websites"

With more than 2.5 quintillion bytes of data \cite{ibm:bigdata} being produced
every day, every now and then we run into a problem of not having 
sufficient computing resources to process and extract useful information
within the required time-frame.

@@

The term big-data is more relevant today because 90\% \cite{ibm:bigdata}
of the data in the world today has been created in the last two years and 
hence big-data is getting a lot of hype from business publications and IT blogs
and the mainstream media.

@@

According to IBM, the challenges of big-data spans three dimensions: Volume,
Velocity and Variety.\cite{ibm:bigdata}

@@

\cite{ibm:bigdata}

@@

\begin{itemize}
  \item \emph{On-demand self services.} Provision resources without human
     interaction with service provider
  \item \emph{Broad network access.} Resources available over the network
  \item \emph{Resource pooling.} Resources are pooled to serve multiple 
        consumers using a multi-tenancy model
  \item \emph{Rapid elasticity.} Ability to increase or decrease resource consumption
  \item \emph{Measured service.} Resource usage can be monitored, controlled and reported.
\end{itemize}

@@

@@

>>>>

With more than 2.5 quintillion bytes of data \cite{website:ibm-bigdata} being produced
every day, every now and then we run into a problem of not having 
sufficient computing resources to process and extract useful information
within the required time-frame.

@@

The term big-data is more relevant today because 90\% \cite{website:ibm-bigdata}
of the data in the world today has been created in the last two years and 
hence big-data is getting a lot of hype from business publications and IT blogs
and the mainstream media.

@@

According to IBM, the challenges of big-data spans three dimensions: Volume,
Velocity and Variety.\cite{website:ibm-bigdata}

@@

\cite{website:ibm-bigdata}

@@

\begin{itemize}
  \item \emph{On-demand self services} \\ Provision resources without human
     interaction with service provider
  \item \emph{Broad network access} \\Resources available over the network
  \item \emph{Resource pooling.} Resources are pooled to serve multiple 
        consumers using a multi-tenancy model
  \item \emph{Rapid elasticity} \\Ability to increase or decrease resource consumption
  \item \emph{Measured service} \\Resource usage can be monitored, controlled and reported.
\end{itemize}

There are three common ways to deploy the Cloud:

\begin{enumerate}
 \item \emph{Private Cloud} \\The Cloud resources are available only 
to a single organization and it is owned and managed by 
that organization or a third party. Typically the infrastructure is in premises of the 
organization.
 \item \emph{Public Cloud} \\The Cloud resources are provisioned for use by the general 
public and the infrastructure is owned, managed and operated by the Cloud provider.
  \item \emph{Hybrid Cloud} \\The Cloud infrastructure is a combination of 
both the private Cloud and the public Cloud with support for data and application 
portability.
\end{enumerate}

@@

The open source Apache Hadoop software library is a framework that 
allows the distributed processing of large data sets across clusters of 
computers using the MapReduce programming model \cite{website:apache-hadoop}. It also provides 
a distributed ﬁle system, the Hadoop Distributed File System, that provides 
high-throughput access to application data.

@@

Google introduced the MapReduce to crunch its huge data sets. 
It is a programming model and an associated implementation for processing 
and generating large data sets. Users specify a map function that processes a 
key/value pair to generate a set of intermediate key/value pairs, and a reduce 
function that merges all intermediate values associated with the same 
intermediate key. MapReduce runs on a large cluster of commodity machines 
and is highly scalable \cite{dean2008mapreduce}.
